On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-02-21 MS.tex
Change in references

\begin{table}[h!]
\centering
\caption{Hypothesised effects of traits on key elements of plant function determining growth rate, as described in eq. \ref{eq:eq0} -- \ref{eq:eq4}. Arrows indicate the effect an increase in trait value would have on each element of the equations, with dashes indicating no effect. Traits are: specific leaf area (= SLA), wood density (= WD), Maximum height (= Hmax), Seed mass, and Maximum photosynthesis per unit leaf area (= Area) For further details, see main text.}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{lllcccccc}
  \hline
  & & & {\bf Symbol} & {\bf SLA} & {\bf WD} & {\bf Hmax} & {\bf Seed mass} & {\bf Aarea} \\ \hline
  \\
  \multicolumn{9}{ l } {\textbf{Elements of equations \ref{eq:eq0} -- \ref{eq:eq4}}}  \\
  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\ud A_{\rm l} / \ud M_{\rm t}$ & \\
    & &     \tabitem leaf  &  & $\uparrow$ & - & - & - & - \\
    & &     \tabitem sapwood & & - & $\downarrow$ & - & - & - \\
    & &     \tabitem root & & - & - & - & - & - \\
  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\ud M_{\rm t} / \ud B$ & - & - & $\uparrow$ & - & - \\
  & & & & & & \\
  & \multicolumn{2}{ l } {Net live biomass production} & $\ud B / \ud t$ & & & & & \\
  & &     \tabitem photosynthesis & & - & - & - & - & $\uparrow$  \\
  & &     \tabitem respiration   & & - & - & - & - & $\uparrow$  \\
  & &     \tabitem leaf turnover & & $\downarrow$ & - & - & - & - \\
  & \multicolumn{2}{ l } {Architecture} & $\ud H / \ud A_{\rm l}$ & - & - & - & - & - \\
  & \multicolumn{2}{ l } {Sapwood area per leaf} & $ \ud A_{\rm ss} / \ud A_{\rm l}$ & - & - & - & - & - \\
  & \multicolumn{2}{ l } {Sapwood turnover} & $k_{\rm ss} \, A_{\rm ss}$ & - & - & - & - & - \\ \hline
  \\
  \multicolumn{9}{ l } {\textbf{Predicted effect on plant growth rate} (small plant {\sepp} large plant)} \\
  & \multicolumn{2}{ l } {in mass} \\
  & & \tabitem{Absolute} & $\ud M_{\rm t} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & & \tabitem{Relative} & $\ud M_{\rm t} / \ud t / M_{\rm t}$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & \multicolumn{2}{ l } {in height} \\
  & & \tabitem{Absolute} & $\ud H / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & & \tabitem{Relative} & $\ud H / \ud t / H$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & \multicolumn{2}{ l } {in diameter} \\
  & & \tabitem{Absolute} & $\ud D / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & & \tabitem{Relative} & $\ud D / \ud t / D$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
\hline
  \end{tabular}
  }
\label{tab:trade-offs}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{Hypothesised effects of traits on key elements of plant function determining growth rate, as described in eq. \ref{eq:eq0} -- \ref{eq:eq4}. Arrows indicate the effect an increase in trait value would have on each element of the equations, with dashes indicating no effect. Traits are: specific leaf area (= SLA), wood density (= WD), Maximum height (= Hmax), Seed mass, and Maximum photosynthesis per unit leaf area (= Area) For further details, see main text.}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{lllcccccc}
  \hline
  & & & {\bf Symbol} & {\bf SLA} & {\bf WD} & {\bf Hmax} & {\bf Seed mass} & {\bf Aarea} \\ \hline
  \\
  \multicolumn{9}{ l } {\textbf{Elements of equations \ref{eq:eq0} -- \ref{eq:eq4}}}  \\
  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\ud A_{\rm l} / \ud M_{\rm t}$ & \\
    & &     \tabitem leaf  &  & $\uparrow$ & - & - & - & - \\
    & &     \tabitem sapwood & & - & $\downarrow$ & - & - & - \\
    & &     \tabitem root & & - & - & - & - & - \\
  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\ud M_{\rm t} / \ud B$ & - & - & $\uparrow$ & - & - \\
  & & & & & & \\
  & \multicolumn{2}{ l } {Net live biomass production} & $\ud B / \ud t$ & & & & & \\
  & &     \tabitem photosynthesis & & - & - & - & - & $\uparrow$  \\
  & &     \tabitem respiration   & & - & - & - & - & $\uparrow$  \\
  & &     \tabitem leaf turnover & & $\downarrow$ & - & - & - & - \\
  & \multicolumn{2}{ l } {Architecture} & $\ud H / \ud A_{\rm l}$ & - & - & - & - & - \\
  & \multicolumn{2}{ l } {Sapwood area per leaf} & $ \ud A_{\rm ss} / \ud A_{\rm l}$ & - & - & - & - & - \\
  & \multicolumn{2}{ l } {Sapwood turnover} & $k_{\rm ss} \, A_{\rm ss}$ & - & - & - & - & - \\ \hline
  \\
  \multicolumn{9}{ l } {\textbf{Predicted effect on plant growth rate} (small plant {\sepp} large plant)} \\
  & \multicolumn{2}{ l } {in mass} \\
  & & \tabitem{Absolute} &  $\ud M_{\rm t} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & & \tabitem{Relative} & $\ud M_{\rm t} / \ud t . M_{\rm t}$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & \multicolumn{2}{ l } {in height} \\
  & & \tabitem{Absolute} & $\ud H / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & & \tabitem{Relative} & $\ud H / \ud t / H$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & \multicolumn{2}{ l } {in diameter} \\
  & & \tabitem{Absolute} & $\ud D / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
  & & \tabitem{Relative} & $\ud D / \ud t / D$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
\hline
  \end{tabular}
  }
\label{tab:trade-offs}
\end{table}
